---
title: "Michael C. Samuel, DrPH"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# https://mcsamueldatasci.github.io/callingCard/
# https://michael-samuel-epidata.netlify.app/

# https://app.netlify.com/sites/michael-samuel-epidata/settings/domain
# mcSamuelDatasci.github.io/callingCard
# https://holtzy.github.io/Pimp-my-rmd/

# https://gt.rstudio.com/


# https://covid19datahub.io/
# https://appsilon.com/ 
# https://appsilon.com/blog/ (good training resources?)


# library(readr)
# covid <- read_csv("COVID-19_Case_Surveillance_Public_Use_Data.csv")


```

```{=html}
<style type="text/css">

body{/* Normal  */
     font-size: 16px;}

h1.title {font-size: 25px;
          color: DarkRed;
          font-family: "Times New Roman";
          margin-top: 30px;}

h1 {/* Header 1 */
  font-size: 18px;}

h2 { /* Header 2 */
    font-size: 20px;
    color: DarkRed;}

</style>
```
<br>

# Senior Epidemiologist / Data Scientist

-   California Department of Public Health
-   University of California San Francisco

# Example Projects and Activities

-   <a target="_blank" rel="noopener noreferrer" href="https://skylab.cdph.ca.gov/communityBurden/">Key work project: California Community Burden of Disease Engine</a>
-   <a target="_blank" rel="noopener noreferrer" href="https://github.com/mcSamuelDataSci/">GitHub Site</a>
-   <a target="_blank" rel="noopener noreferrer" href="https://scholar.google.ca/citations?view_op=list_works&hl=en&user=eP0-Z04AAAAJ&gmla=AJsN-F6_KIIXGk6cFMgGswLXImQ0vopI6uIwDh7J17jKe3peyLK-xNjczktM_-9xDf-WHCrFVlYM-eXzatKdjfS-fdul8le5LG1ihZ0k3eD-7eoWxmQVv0Fxi0Z1-3xjJBNSW8XkNhwk">Publications</a>
-   <a target="_blank" rel="noopener noreferrer" href="https://goo.gl/wgLkoR">Visual Display Workshops</a>

# Education

-   DrPH - Biostatistics/Epidemiology, University of California, Berkeley
-   MPH - Biostatistics, University of California, Berkeley
-   B.S. - Conservation and Resource Studies, University of California, Berkeley

# Contact

-   [Michael.Samuel\@cdph.ca.gov](mailto:Michael.Samuel@cdph.ca.gov){.email}
-   [samfam921\@gmail.com](mailto:samfam921@gmail.com){.email}
-   cell 925.285.2926

<br>

# A reasonably normal guy

```{r echo = FALSE, fig.height=.8, fig.width=2}
library(ggplot2)

tDat <- data.frame(myDat = rnorm(1000))


ggplot(data=tDat, aes(x=myDat)) + geom_density(linewidth=1.2,fill="cyan") + theme_void()
```
