---
title: "Michael C. Samuel, DrPH"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<style type="text/css">

body{/* Normal  */
     font-size: 16px;}

h1.title {font-size: 25px;
          color: DarkRed;
          font-family: "Times New Roman";
          margin-top: 30px;}

h1 {/* Header 1 */
  font-size: 18px;}

h2 { /* Header 2 */
    font-size: 20px;
    color: DarkRed;}

</style>

 

<br>

# Senior Epidemiologist / Data Scientist

*  California Department of Public Health
*  University of California San Francisco


# Example Projects and Activities


*  <a target="_blank" rel="noopener noreferrer" href="https://discovery.cdph.ca.gov/fusion/communityburden/)">Key work project:  California Community Burden of Disease Engine</a>
*  <a target="_blank" rel="noopener noreferrer" href="https://github.com/mcSamuelDataSci/">GitHub Site</a>
* <a target="_blank" rel="noopener noreferrer" href="https://scholar.google.ca/citations?view_op=list_works&hl=en&user=eP0-Z04AAAAJ&gmla=AJsN-F6_KIIXGk6cFMgGswLXImQ0vopI6uIwDh7J17jKe3peyLK-xNjczktM_-9xDf-WHCrFVlYM-eXzatKdjfS-fdul8le5LG1ihZ0k3eD-7eoWxmQVv0Fxi0Z1-3xjJBNSW8XkNhwk">Publications</a>
*  <a target="_blank" rel="noopener noreferrer" href="https://dlab.berkeley.edu/people/dr-michael-samuel">Visual Display Workshops</a>


#  Education 
*  DrPH - Biostatistics/Epidemiology, University of California, Berkeley
*  MPH  - Biostatistics, University of California, Berkeley 
*  B.S. - Conservation and Resource Studies,  University of California, Berkeley


# Contact
*  Michael.Samuel@cdph.ca.gov
*  samfam921@gmail.com
*  cell 925.285.2926

<br>

# A reasonably normal guy

```{r echo = FALSE, fig.height=.8, fig.width=2}
library(ggplot2)

tDat <- data.frame(myDat = rnorm(1000))


ggplot(data=tDat, aes(x=myDat)) + geom_density(size=1.2,fill="cyan") + theme_void()
```










